\documentclass{muratcan_cv}
\setname{Ashish}{Patel}
\setaddress{Bengaluru, India}
\setmobile{+91 7705047900}
\setmail{ashishpatel0720@gmail.com}
\setposition{BigData Engineer} %ignored for now
\setlinkedinaccount{https://linkedin.com/in/ashishpatel0720/}
\setportfolio{https://ashish.live/}

%you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/pateash} %you can play with color of the template (red is also nice..)
\setthemecolor{cyan} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{ Experienced Software Engineer experience in \textbf{Big Data}, \textbf{Distributed Systems}, \textbf{Java}, \textbf{Scala} and \textbf{Python} seeking to apply my abilities to contribute and build something productive.\\
I am an active contributor to \textbf{Apache Airflow}.
}
% Experience
\section{Experience}
    % Prophecy
    \datedexperience{Prophecy.io}{Jan, 2023 - Present / Bengaluru, India}
		\explanation{Senior Data Engineer}\\
		\explanationdetail{\coloredbullet\
	 Building High-Quality Scalable ETL Frameworks and Pipelines using cutting edge solutions.
	 }
		\explanationdetail{\coloredbullet\
	 working as Solutions Architect and helping our customers creating best frameworks to simpilify their data pipelines.
	 }
  \explanationdetail{\coloredbullet\
		\textbf{Tech Stack} - Apache Spark, Apache Airflow, Python, Scala, Databricks, Snowflake and DBT.
		}
    % Skyscanner
\datedexperience{Skyscanner}{Dec, 2021 - Jan, 2023 / London, UK}
		\explanation{Senior Software Engineer ( Distributed Systems ) }\\
		\explanationdetail{\coloredbullet\
	 Building High-Quality Scalable ETL Frameworks and Pipelines using cutting edge solutions like \textbf{Databricks}, \textbf{ Apache Spark}, \textbf{DeltaLake},  \textbf{Apache  Airflow} and \textbf{AWS}.
	 }
        \explanationdetail{\coloredbullet\
		Working on cutting edge big data solutions to enable our Data Analysts and Data Scientists to make sense of revenue data and Clickstream data.}
		\explanationdetail{\coloredbullet\
	 Building High Scalable Streaming Pipelines using cutting edge solutions like \textbf{Apache Kafka} and \textbf{AWS MSK}.
	 }

  \explanationdetail{\coloredbullet\
		\textbf{Tech Stack} - Apache Spark, Apache Airflow, Databricks, DeltaLake, Python and Java
		}
		    % Apache Airflow
    \datedexperience{Apache Airflow}{Feb, 2021 - Present / Remote}
		\explanation{Open Source Contributor}

        \explanationdetail{\coloredbullet\
		\href{https://github.com/apache/airflow/commits?author=pateash}{Contributed} \textbf{12+} Pull requests to Opensource \href{https://github.com/apache/airflow}{Airflow} repository on Github.}
    \explanationdetail{\coloredbullet\
	Participated and contributed in Meetups and discussions to make Apache Airflow one of the best Open Source Orchestration platform.}

    % WALMART LABS
    \datedexperience{Walmart Global Tech}{Feb, 2021 - Dec, 2021 / Bangalore, India}
		\explanation{Software Engineer III (Big Data) }

        \explanationdetail{\coloredbullet\
		Part of the \textbf{supply chain technology} team, and working on cutting edge forecasting solutions to enable the everyday low-cost philosophy of Walmart.}
		\explanationdetail{\coloredbullet\
	 Built High-Quality Scalable ETL Frameworks and Pipelines to build our Forecasting Pipelines.
	 }
      \explanationdetail{\coloredbullet\
	Migrated our On-Prem Hadoop Clusters to Google Cloud Platform as part of a strategic partnership with Google.}
	  \explanationdetail{\coloredbullet\
		\textbf{Tech Stack} - Apache Spark, Java, PySpark, Apache Airflow, GCP DataProc, Bigquery,Astronomer
		}
		\\
	% Deutsche bank
	\datedexperience{Deutsche Bank}{July, 2018 - Jan, 2021 / Pune, India}
	\explanation{Senior Software Engineer}
        \explanationdetail{\coloredbullet\
		Worked As a Big Data engineer in CIB division for Volcker Project.}
        \explanationdetail{\coloredbullet\
		Developed \textbf{Data pipelines for our Reporting ETL} jobs, handling \textbf{Terabytes} of data
every day across hundreds of Spark and Hadoop MapReduce jobs.}
        \explanationdetail{\coloredbullet\
	Optimized End to End Pipeline execution time to comply with Regulatory SLA in
accordance with new Volcker2.0 regulatory Norms.}
        \explanationdetail{\coloredbullet\
	Developed Platform simplification for Informatica jobs using Java8 and Spring +
Reactor Framework with Oracle Database.}
        \explanationdetail{\coloredbullet\
	\textbf{Tech Stack} - Apache Spark, Hadoop MapReduce, Hive, Impala, Beeline, Cloudera CDH,
Java, Spring Framework, Spring Boot, Scala, Linux, GCP.}\\
	% NIT, Bhopal
	\datedexperience{NIT, Bhopal}{Oct, 2017 - Feb, 2018 / Bhopal, India}
	\explanation{Research Assistant}
        \explanationdetail{\coloredbullet\
		Co-written  \textbf{\itshape{"A Comparative Study of Music Recommendation Systems"}} with
Prof. Rajesh Wadhvani.}
    \explanationdetail{\coloredbullet\
		This paper describes different recommendation strategies and compares their
practicality on mobile devices.}
    \explanationdetail{\coloredbullet\
		Evaluated different Recommendation Strategies by training different ML models and
evaluating them.}
    \explanationdetail{\coloredbullet\
		\textbf{Reference} - \textbf{https://ieeexplore.ieee.org/document/8546852}
		}
		\\
	% CARWALE
	\datedexperience{CarWale.com}{May, 2017 - Jul, 2017 / Mumbai, India}
	\explanation{Summer Intern}
        \explanationdetail{\coloredbullet\
		Worked as Data Engineering Intern in the R\&D division of CarWale.}
		 \explanationdetail{\coloredbullet\
		We developed CWBigQuery, which is a service that enables interactive analysis of
massively large datasets stored in Cassandra Storage.}
 		 \explanationdetail{\coloredbullet\
	It allows users to submit and schedule Spark Job, just using SQL like syntax using Spark
SQL.}
 	 \explanationdetail{\coloredbullet\
	This Project took inspiration from Google BigQuery but uses a completely different
architecture, we have also created a web application which will provide an interface for users to log in
and submit, schedule, and view results.}
 	 \explanationdetail{\coloredbullet\
	\textbf{Tech Stack} - Scala, Apache Spark, Cassandra, Python-Flask Framework}


%
%
%Education
\section{Education}
    \datedexperience{NIT, Bhopal}{ 2014 - 2018}
    \explanation{Bachelor of Technology, Computer Science \& Engineering}
     \explanationdetail{\coloredbullet\ %
     Graduated in Computer Science and Engineering.
	\textbf{GGPA} - 8.4/10
	}
	 \explanationdetail{\coloredbullet\ %
	  Worked as Web developer in the Student Council and developed websites and tech infrastructure for College events.
     }

    \datedexperience{I.P.S Academy}{2011 - 2013}
    \explanation{Higher Secondary, Science \& Mathematics}
    \explanationdetail{\coloredbullet\
     Completed Higher Secondary with Physics, Chemistry, and Maths.
	Percentage - 90.2\%     }
%

% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming}{Java\cpshalf Scala\cpshalf Python\cpshalf C++\cpshalf Bash}}
    %
    \newcommand{\skilltwo}{\createskill{Big Data Frameworks}{Apache Spark\cpshalf Kafka\cpshalf Databricks \cpshalf Airflow\cpshalf Snowflake\cpshalf DBT\cpshalf Hive\cpshalf AWS\cpshalf GCP}}
    %
    \newcommand{\skillthree}{\createskill{Software Development}{Spring Framework\cpshalf RDBMS\cpshalf Python Flask\cpshalf  Agile\cpshalf DevOps}}
    %
    \newcommand{\skillfour}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Hindi \cpshalf\ \ \textbf{\emph{Fluent:}} \ \ English }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%

% AWARDS and RECOGNITION
\section{Awards and Recognition}
    \newcommand{\awardone}{
    Competed with 200+ teams and Won 3rd prize in Deutsche Bank's Global DataScience Competition Dabble.\\
    }
    %
    \newcommand{\awardtwo}{
		Won 2nd prize in Hackathon organized by Appointy Inc, https://github.com/pateash/appointy-hackathon\\
		}
    %
        \newcommand{\awardthree}{
    Winner of Deutsche bank's excellence award.\\
    }
    %

    \newcommand{\awardfour}{
    	Winner of Medhavi Chhatra Puruskar, given by MP State Government for excellent performance in State board exams.}
    %

	%
    \newcommand{\listofawards}{\awardone, \awardtwo, \awardthree,  \awardfour}
    %
    \createbullets{\listofawards}
%

% EXTRA
\section{Extra}
%    \newcommand{\extraone}{ Languages - English, Hindi    }
    %
    \newcommand{\extratwo}{
		Contributing to Apache Airflow, contributions - \textbf{https://github.com/pateash}
		}
    %
    \newcommand{\extrathree}{
    	Working on Open source, CMD tool for developers, \textbf{https://github.com/codingtools/cdt}
		}
    %
    \newcommand{\extrafour}{
		Writing Articles on Codebrace on Medium \textbf{https://medium.com/codebrace}, with over \textbf{100K+} reads so far.
		}
    \newcommand{\extrafive}{
		Created Opensource Regexplore, Intuitive Regex Checker \textbf{https://regexplore.github.io}
		}


	%
    \newcommand{\listofextras}{\extratwo, \extrathree,  \extrafour,  \extrafive}
    %
    \createbullets{\listofextras}
%
%Footnote
\createfootnote
\end{document}
